Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-03-16 paper.tex
update

To compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in web services composition obtained through two different methods. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two composition weighted graphs as the two optimised solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure where those service vertices and edges denoted in red are different. We make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertices in terms of quality of semantic matchmaking and QoS attributes in Fig. \ref{comparisontest} $(3)$. We also look at $\Delta Q$ which reveals the amount of variation on quality between two methods, where the positive values means the benefits gained under our approach while the negative values means the tradeoff. To demonstrate the benefits of the positive value, we analyse the smallest positive $\Delta Q$ corresponding to $e_4$ and demonstrate how the output and required input are different under two approaches in Fig. \ref{comparisontest} $(4)$. $Ser1640238160$ and $Ser1947554374$ are selected service vertices with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' requirements suggesting that our method can produce better semantic matchmaking quality in terms of less general outputs.

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparisontest}
\end{figure}

@@

The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods. We employ statistical analysis to test the significant differences in mean fitness value.  The results show that the PSO-based approach performs better in four of five tasks.

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$ (P:0.000)  &0.520659 $\pm$ 0.020758           \\ \hline
WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$ (P:0.008)   &0.459681 $\pm$  0.002874          \\ \hline
WSC09 03                     & 0.550396 $\pm$ 0.012780                        &0.567915 $\pm$ 0.023447 $\uparrow$  (P:0.000) \\ \hline
WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$ (P:0.003)  &0.431704 $\pm$ 0.009774            \\ \hline
WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$ (P:0.000)  &0.245222 $\pm$ 0.036885            \\ \hline
\end{tabular}
\end{table}

>>>>

To better understand that our evaluation approach could generate solutions having better semantic matchmaking quality with a slight trade off in $QoS$, we demonstrate an example solution to Task 3. Fig. \ref{comparisontest} $(1)$ and $(2)$ show two weighted DAGs as two solutions employing QoS-aware approach and Comprehensive quality-aware method respectively. Two approaches generate exactly the same service workflow structure while some service vertices and edges denoted in red are different. We list the semantic matchmaking quality represented by all edges ($e_1$ to $e4$) and overall QoS in Fig. \ref{comparisontest} $(3)$. To demonstrate how different the semantic matchmaking quality is, we analyse $e_4$ that has the smallest $\Delta Q$, which reveals the smallest semantic matchmaking quality gained using our approach. $e_4$ has two different source service vertices ($Ser1640238160$ and $Ser1947554374$) and two same $end$ vertices . Further more, in Fig. \ref{comparisontest} $(4)$, $Ser1640238160$ and $Ser1947554374$ are service with output concept-related parameters $Inst795998200$ and $Inst582785907$ corresponding to two concepts $Con103314376$ and $Con2037585750$ respectively, and $Inst658772240$ are the required parameter for the $end$ vertice, which is related to concept $Con2113572083$. There exist $Inst795998200$ $\in$ $Con103314376$ $\sqsubseteq_{2}$ $Inst658772240$ $\in$ $Con2113572083$ and $Inst582785907$ $\in$ $Con2037585750$ $\sqsubseteq_{3}$ $Inst658772240$ $\in$ $Con2113572083$. It is obvious that our approach selects the service providing $Inst795998200$ that are closer to the users' required outputs.
\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}

@@

The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods. We employ statistical analysis to test the significant differences in mean fitness value. The results show that the PSO-based approach performs better in four of five tasks (all the p-values are consistently smaller than 0.01).

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &0.559207 $\pm$ 0.012780  $\uparrow$   &0.520659 $\pm$ 0.020758           \\ \hline
WSC09 02                     &0.470083 $\pm$  0.001106 $\uparrow$   &0.459681 $\pm$  0.002874          \\ \hline
WSC09 03                     & 0.550396 $\pm$ 0.012780                        &0.567915 $\pm$ 0.023447 $\uparrow$   \\ \hline
WSC09 04                     & 0.468942 $\pm$ 0.001670  $\uparrow$   &0.431704 $\pm$ 0.009774            \\ \hline
WSC09 05                     & 0.469424 $\pm$ 0.000800  $\uparrow$   &0.245222 $\pm$ 0.036885            \\ \hline
\end{tabular}
\end{table}
